% netlist
\section{Working with \texttt{gnetlist}}

\subsection{Generating a netlist}

The command
\begin{center}
  \texttt{gnetlist -g PCB <input.sch> -o <output.net>}
\end{center}
will create a netlist readable by both you and PCB. The file will have
three columns: net name, starting pin, and ending pin.


\subsection{Generating a bill of materials (BOM)}
The \texttt{-g} flag for gnetlist allows you to specify a guile script
to be run.  Scripts for BOM creation are located in
\verb8/usr/share/gEDA/scheme8, and some are described in table
\ref{bom_scripts}.  \input{bom_table}


For example, the command
\begin{center}
  \texttt{gnetlist -g bom <input.sch> -o <output.bom>}
\end{center}
will generate a BOM.  You must have a file called ``attribs'' in the
directory from which gnetlist is invoked.  This file should just
contain a column of attributes you want included in the BOM.  An
example is:


\begin{center}
  \begin{minipage}{2cm}
    \verbatiminput{attribs}
  \end{minipage}
\end{center}


\subsection{Design rule checks}

\subsubsection{Checking for duplicated reference designators}
You can check for duplicated reference designators using the
\texttt{drc2} backend.  Use this command:

\boxcmd{ \$ gnetlist -g drc2 -o errors.drc
  schem1.sch schem2.sch ...  }

You'll have to accept that multi-symbol parts will generate errors, since they necessarily have the same reference designators.  Still, single-symbol parts with repeated references designators really are errors that should be corrected.  There seem to be ways to suppress different kinds of error checks, but I can't get them to work.

