\section{Using the Flip software}
FLIP stands for FLexible In-system Programmer.  The FLIP software facilitates 
downloading of firmware images to the target using the preprogrammed 
bootloader.

\subsection{Using FLIP under Linux}
FLIP is a Java application, and as such can be made to run on Linux-based 
machines.  

\subsubsection{Installing FLIP with Java already configured}
If your Java Virtual Machine (JVM) is already installed and configured, follow 
these steps to install FLIP:
\begin{enumerate}
	\item Copy the \verb+flip_linux_3-2-1.tgz+ archive to a reasonable 
	location (I like \verb+/usr/share+) and extract it.
	\item Set some environment variables (I like to do this in my 
	\verb+.bashrc+ file).
	\begin{enumerate}
		\item \verb+FLIP_PATH = /usr/share/flip.3.2.1+
		\item \verb+FLIP_HOME = /usr/share/flip.3.2.1/bin+
		\item \verb+JAVE_HOME = /opt/sun-jdk-1.6.0.13+ (You can use 
			\verb+java-config --jdk-home+ to tell you the proper \verb+JAVA_HOME+ 
			location)
	\end{enumerate}	
\end{enumerate}


\subsubsection{Invoking FLIP}
Once FLIP is installed, there are some quirks to invoking it:
\begin{enumerate}
	\item \verb+cd /usr/share/flip.3.2.1/bin+ (You have to actually change to 
	this directory for FLIP to find everything it needs.
	\item \verb+flip.sh+
\end{enumerate}

\subsubsection{Using FLIP with the STK526 evaluation board}
FLIP will not recognize the AVR target processor when the STK526 board is 
first connected via USB.  The target must first be forced to run its 
bootloader code.  Hold down the ``HWB'' button while tapping ``RST'' once to 
force the AVR to execute its bootloader code.

\subsubsection{Burning a firmware image}
Once FLIP has initialized communication with your device running bootloader 
code, it's time to transfer a firmware image.  FLIP will work with Intel HEX 
file formats to begin the Device Firmware Upgrade (DFU) process.  These files 
typically have the \verb+*.hex+ or \verb+*.a90+ file extensions.

Sample images are supplied with the STK526 evaluation board on the ``USB 
Products'' CD.  The sample mouse application is archived in
\begin{center}
\verb+/starterkits/STK526/Firmware+
\end{center}
along with it's firmware image in the \verb+/hex+ directory.
